The past and future of visualization for computing in science and engineering

### 2020-04-05 CombaWeiskopf2020/paper.tex
edit fig.3 includegraphics
edits sent by Daniel

The VizCorner has also covered projection techniques that reduce multidimensional data to 2D data for visualization purposes, including user-centered control of the projection techniques, and showing multiple data dimensions simultaneously via parallel coordinates. Papers in this category often include generic visualizations that can be useful in many areas of science and engineering.

@@

A classic research area, flow visualization considers input from flow simulation and experiments alike. Our pick from the VizCorner is by Grzegorz Karch and colleagues~\cite{Karch2012}, who described methods for high-quality flow visualization utilizing the metaphor of dye advection. Experimental flow visualization has a long tradition of dye-based observations. Its computational counterpart uses the same idea now in a computer-based visualization; see an example in Figure~\ref{fig:karman}.

@@

\begin{figure*}
    \begin{center}    
        \includegraphics[width=0.40\textwidth]{museum1.png} %\hspace{-3em} \raisebox{12ex}{\includegraphics[width=0.5\textwidth]{museum2.png}}
        \includegraphics[width=0.48\textwidth]{museum2.png}
        \caption{Interactive table with a plankton visualization. Image: \copyright{} 2016 IEEE, reprinted from Sauer et al.~\cite{Sauer2016}. 
  \label{fig:museum}}        
    \end{center}
\end{figure*}

>>>>

The VizCorner has also covered projection techniques that reduce multidimensional data to 2D data for visualization purposes or methods that show multiple data dimensions simultaneously via parallel coordinates. Papers in this category often include generic visualizations that can be useful in many areas of science and engineering.

@@

A classic research area of scientific visualization, flow visualization considers input from flow simulation and experiments alike. Our pick from the VizCorner is by Grzegorz Karch and colleagues~\cite{Karch2012}, who described methods for high-quality computational flow visualization utilizing the metaphor of dye advection. Experimental flow visualization has a long tradition of dye-based observations. Its computational counterpart uses the same idea now in a computer-based visualization; see an example in Figure~\ref{fig:karman}.

@@

\begin{figure*}
    \begin{center}    
        \includegraphics[width=\textwidth]{museum.png} 
        \caption{Interactive table with a plankton visualization. Image: \copyright{} 2016 IEEE, reprinted from Sauer et al.~\cite{Sauer2016}. 
  \label{fig:museum}}        
    \end{center}
\end{figure*}
